---
title: "Data weighting in SS" 
author: "Johnson, K.F., Doering, K.L., Taylor, I.G., and Wetzel, C.R."
date: "Last update: `r format(Sys.time(), '%d %B, %Y')`" 
output:
  html_document:
    toc: true
    toc_float:
        collapsed: true
        smooth_scroll: true
    toc_depth: 3
    fig_caption: yes
    code_folding: show
    number_sections: true

fontsize: 12pt
---

# Introduction
Todo: read Punt and Francis papers.

# Methods
```{r settings}
thedir <- "c:/Users/kelli/Documents/ss3sim_nin"
niter <- 10
fixx <- c(1, 2)
fixn <- seq(25, 200, by = 25)
name.om <- "hakeom"
name.em <- "hakeem"
library(ggplot2)
devtools::load_all("c:/stockAssessment/SS/ss3sim")
```
```{r createem, eval = FALSE, echo = FALSE}
setwd(thedir)
# Create the EM from the OM
ss3sim::create_em(dir_in = file.path(thedir, hake.om),
  dir_out = file.path(thedir, hake.em))

```
```{r scenarios}
vals <- paste0("c(", outer(fixx, fixn, paste, sep = ","), ")")
grid <- expand.grid(fixx, fixn)
scen <- data.frame(
  "cf.years.1" = "26:100",
  "cf.fvals.1" = 0.747,
  "si.years.2" = "seq(76, 100, by = 1)",
  "si.sds_obs.2" = 0.2,
  "sl.Nsamp.1" = 50,
  "sl.Nsamp.2" = 50,
  "sl.years.1" = "seq(26, 100, by = 1)",
  "sl.years.2" = "seq(76, 100, by = 1)",
  "sl.cpar" = "NULL",
  "sa.Nsamp.1" = 100,
  "sa.Nsamp.2" = 100,
  "sa.years.1" = "seq(26, 100, by = 1)",
  "sa.years.2" = "seq(76, 100, by = 1)",
  "sa.cpar" = "NULL",
  "wc.method" = "DM",
  "wc.fleets" = "1:2",
  "co.par_name" = 'c("Age_DblN_peak_Survey(2)")',
  "ce.par_name" = 'c("AgeSel_P_1_Survey")',
  "ce.par_phase" = "c(NA)",
  "om" = file.path(thedir, name.om),
  "em" = file.path(thedir, name.em)
)
scen.all <- data.frame(scen,
  "co.par_int" = grid[, 1],
  "sl.ESS" = grid[, 2])
# Set scenario names if you want
scen.all[, "scenarios"] <- paste0("nin-", seq(1,NROW(scen.all)))
```

```{r run, eval = FALSE}
run_ss3sim(iterations = 1:niter, simdf = scen.all)
get_results_all()
```
```{r plotsetup, echo = FALSE}
sc <- read.csv(dir(pattern = "scalar"))
ts <- read.csv(dir(pattern = "ts"))
scre <- calculate_re(sc)
scre$Nin <- scen.all[match(scre$scenario, scen.all$scenario), "sl.ESS"]
scre$dm_1 <- with(scre, exp(ln_DM_theta_1_em)/(1+exp(ln_DM_theta_1_em))) * scre$Nin
scre$dm_2 <- with(scre, exp(ln_DM_theta_2_em)/(1+exp(ln_DM_theta_2_em))) * scre$Nin
scre$dm_3 <- with(scre, exp(ln_DM_theta_3_em)/(1+exp(ln_DM_theta_3_em))) * scen.all$sa.Nsamp.1[1]
scre$dm_4 <- with(scre, exp(ln_DM_theta_4_em)/(1+exp(ln_DM_theta_4_em))) * scen.all$sa.Nsamp.2[1]
```

# Results
  * Input sample sizes smaller than the true value will always lead to underestimation of the true sample size
  * As input sample sizes become more positively biased relative to the true sample size, the estimated effective sample size becomes more negatively biased
  * Error in estimates of effective sample size lead to error in estimates of growth parameters
  * Estimation of age-composition weightings are independent of succesfull estimation of length-composition weightings

# Tables
Tables suck.

# Figures

## Figures with captions
```{r plotsdmlength, echo = FALSE, fig.cap = "Effective sample sizes for length-composition data after estimating Dirichlet-Multinomial (DM) relative weighting parameters. Colors indicate the input sample size and solid green lines are the true sample size used in the operating model (OM). Columns reflect a change in survey selectivity in the OM. Note the change in the scale for each y axis."}
gg <- plot_points(data = scre, x = "dm_1", y = "dm_2", 
  vert = "Age_inflection_Survey_2_om", horiz = "Nin",
  color = "Nin", print = FALSE) + 
xlab("Fishery length-composition effective sample size after DM estimation") +
ylab("Survey length-composition effective sample size after DM estimation") +
labs(title = "Operating model survey selectivity age of inflection",
  col = "Length\ncomp\ninput N") +
geom_hline(yintercept = 50, col = "dark green") +
geom_vline(xintercept = 50, col = "dark green")
print(gg)
```

```{r plotsdmage, echo = FALSE, fig.cap = "Effective sample sizes for age-composition data after estimating Dirichlet-Multinomial (DM) relative weighting parameters. Colors indicate the input sample size for length-composition data, where the true was 50, and solid green lines are the true sample size used in the operating model (OM). Columns reflect a change in survey selectivity in the OM."}
gg <- plot_points(data = scre, x = "dm_3", y = "dm_4", 
  vert = "Age_inflection_Survey_2_om", horiz = "Nin",
  color = "Nin", axes.free = FALSE, print = FALSE) + 
xlab("Fishery age-composition effective sample size after DM estimation") +
ylab("Survey age-composition effective sample size after DM estimation") +
labs(title = "Operating model survey selectivity age of inflection",
  col = "Length\ncomp\ninput N") + 
geom_hline(yintercept = 100, col = "dark green") +
geom_vline(xintercept = 100, col = "dark green")
print(gg)
```

## Figures without captions
```{r plotsm, echo = FALSE}
gg <- plot_points(data = scre, x = "NatM_p_1_Fem_GP_1_em", y = "Age_inflection_Survey_2_em",
  vert = "Age_inflection_Survey_2_om", #horiz = "Nin",
  col = "Nin", axes.free = FALSE, print = FALSE) +
  geom_vline(xintercept = 0.21) +
labs(title = "Operating model survey selectivity age of inflection",
  col = "Length\ncomp\ninput N")
print(gg)
gg <- plot_points(data = scre, x = "VonBert_K_Fem_GP_1_em", y = "L_at_Amax_Fem_GP_1_em",
  vert = "Age_inflection_Survey_2_om", #horiz = "Nin",
  col = "Nin", axes.free = FALSE, print = FALSE) +
  geom_vline(xintercept = scre[1,"VonBert_K_Fem_GP_1_om"], col = "dark green") +
  geom_hline(yintercept = scre[1,"L_at_Amax_Fem_GP_1_om"], col = "dark green") +
  labs(title = "Operating model survey selectivity age of inflection",
    col = "Length\ncomp\ninput N") +
  xlab(expression(hat(K))) +
  ylab(expression(hat(L~at~max~age)))
print(gg)
gg <- plot_points(data = scre, x = "Age_95.width_Fishery_1_em", y = "Age_95.width_Survey_2_em",
  vert = "Age_inflection_Survey_2_om", #horiz = "Nin",
  col = "Nin", axes.free = FALSE, print = FALSE) +
  geom_vline(xintercept = scre[1,"Age_95.width_Fishery_1_om"], col = "dark green") +
  geom_hline(yintercept = scre[1,"Age_95.width_Survey_2_om"], col = "dark green") +
labs(title = "Operating model survey selectivity age of inflection",
  col = "Length\ncomp\ninput N") +
  xlab(expression(hat(Fishery~age~at~peak))) +
  ylab(expression(hat(Survey~age~at~peak)))
print(gg)
```
